Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-05-31 EMNLP-demo-paper/conclusion.tex
minor fix

\section{Discussion}
In this work, we introduce a visualization library for creating customized environments that allow the user to interrogate the relationship between different parts of the model pipeline via interactive queries.
%
We demonstrate the usability and flexibility of tool by configuring the visual components to investigate models for solving different NLP tasks (e.g., NLI, MC).
%
We also conducted a small-scale user evaluation, where we ask five Ph.D. level students with NLP background to spend 30 minutes with the tool and then provide feedback. Most suggest the environment allow them to refine queries iteratively and identify potential issues with the model, but some student also mentioned the tool might not provide enough guidance for user do not already have an in-depth understanding of the model at hand.

Even though we design the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure the current interface is compatible with all the available configurations.
%
In the future, we plan to improve upon the current attention interface, release the library as an open source package, and expand the visualization components to handle tasks such neural machine translation and more.

>>>>

\section{Discussion}
In this work, we introduce a visualization library for creating customized environments that allow the user to interrogate the relationship between different parts of the model pipeline via interactive queries.
%
We demonstrate the usability and flexibility of tool by configuring the visual components to investigate models for different NLP tasks (e.g., NLI, MC).
%
We also conducted a small-scale user evaluation, where five Ph.D. level students with NLP background spent 30 minutes with the tool and then provided feedback. Most suggested the environment allow them to refine queries iteratively and identify potential issues with the model, but some student also mentioned the tool might not provide enough guidance for users do not have an in-depth understanding of the model at hand.

Even though we design the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure compatibility with all the available configurations.
%
In the future, we plan to improve upon the current attention interface, release the library as an open source package, and expand the visualization components to handle tasks such neural machine translation and more.
